A new method to estimate dark matter halo concentrations

### 2015-08-27 paper/article.tex
revised 3 paragraphs in the intro

\section{Introduction}
\label{sec:introduction}
In the concordance cosmology the matter content of the
Universe is dominated by dark matter, a collisionless fluid shaped by
gravitational interactions.
In the last three decades numerical experiments have made possible the
simulation of dark matter dominated universes, yielding valuable
insights on the large scale structure formation process.
This description shows a remarkable success in comparisons against
observations of galaxy distributions on large scales
\citep{Springel2005,2011ApJ...740..102K}.

Regarding the small scale dark matter distribution, one of the most
striking results of these simulations is that dark matter overdensities
follow a universal density profile.
In a first approximation this profile is spherically symmetric and its
density only dependens on the radial coordinate.
The universality of this profiles seems to be independent of the
cosmological parameters and self-similar for different spatial scales
after an adequate re-scaling is applied.
\citep{NFW,Taylor2001}

One the most popular parameterization for a halo radial density
distribution is known as the Navarro-Frenk-White (NFW) profile
\citep{NFW}.
This profile is a  double power law in radius, where the transition
between the two happens at the so-called scale radius $r_s$.
The ratio between the scale radius and the virial radius of the halo
$R_v$ is known as the concentration $c=R_v/r_s$.
Simulations also show that the concentration is a function of halo
mass.

>>>>

\section{Introduction}
\label{sec:introduction}
In the concordance cosmology paradigm the matter content of the
Universe is dominated by dark matter, a collisionless fluid shaped by
gravitational interactions.
Simulations of dark matter dominated universes during the last three
decades have provided valuable insights into the large scale structure
formation process, showing a remarkable success when theoretical
results are compared against observations of the galaxy distribution
obtained from large surveys.
\citep{Springel2005,2011ApJ...740..102K}.

On galactic scales the most striking results of these simulations is
that dark matter overdensities closely follow a universal density
profile. 
In a first approximation this profile is spherically symmetric and its
density only dependens on the radial coordinate.
The universality of this profiles seems to be independent of the
cosmological parameters and is self-similar for different spatial
scales after an adequate re-scaling is applied. 
\citep{NFW,Taylor2001}

One the most popular parameterization for a halo radial density
distribution is known as the Navarro-Frenk-White (NFW) profile
\citep{NFW}.
This profile is a  double power law in radius, where the transition break
happens at the so-called scale radius $r_s$.
The ratio between the scale radius and the virial radius, $R_v$ which
defines a natural scale for the halo, is known as the concentration
$c=R_v/r_s$. 
Simulations show that the concentration is a strong function of halo mass and
redshift.
